---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mlstrOpalr

<!-- badges: start -->
[![R-CMD-check](https://github.com/maelstrom-research/mlstrOpalr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maelstrom-research/mlstrOpalr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

# mlstrOpalr

The goal of mlstrOpalr is to provide functions to support compatibility between
Maelstrom R packages and Opal environment. Opal is the OBiBa application for 
data management, and Opal environments can be integrated with RStudio 
environments using the package `opalr`. The user must have adequate credentials 
to interact with a specific Opal environment.
Please see [Opal documentation](https://opaldoc.obiba.org/en/dev/) for complete 
documentation.

# Get started

## Install the package

```{r, eval=FALSE}
# To update the R package in your R environment you may first need to remove 
# it, and use the exit command quit() to terminate the current R session.

# To install the R package:
install.packages('mlstrOpalr')
library(mlstrOpalr) 

#if you need help with the package, please use:
mlstrOpalr_help()

```
